\documentclass[12pt,letterpaper]{amsart}

\sloppy

\addtolength{\textwidth}{60pt}
\addtolength{\oddsidemargin}{-32pt}
\evensidemargin\oddsidemargin

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

%PACKAGES
\usepackage{geometry}               
\geometry{letterpaper}                   

%URL colors
\usepackage{color}
\definecolor{myurlcolor}{rgb}{0.6,0,0}
\definecolor{mycitecolor}{rgb}{0,0,0.8}
\definecolor{myrefcolor}{rgb}{0,0,0.8}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks,
  linkcolor=myrefcolor,
  citecolor=mycitecolor,
  urlcolor=myurlcolor}

\begin{document}

\centerline{\large BIOGRAPHICAL SKETCH}
\vskip 1em
\centerline{John C.\ Baez}

\vskip 1em
\vskip 1em

%---------------------------------
\textbf{Professional preparation}

\vskip 1em

\begin{itemize}
\item
  Princeton University, Princeton:  B.A., Mathematics, 1982.
\item
  Massachusetts Institute of Technology, Cambridge: Ph.D., Mathematics, 1986. 
\end{itemize}

%---------------------------------
\textbf{Appointments}

\vskip 1em

\begin{itemize}
\item
  2010--Present: Visiting Researcher, Center for Quantum Technologies.
\item
  1990--Present: Professor, University of California, Riverside.
\item
  1988--1990: Assistant Professor, University of California, Riverside.
\item
  1986--1988: Instructor, Yale University.
\end{itemize}

%------------------------------------
\textbf{Five products most closely related to the proposed project}

\vskip 1em 

\begin{itemize}
\item
  John C.\ Baez and Mike Stay.
  \href{http://arxiv.org/abs/0903.0340}{Physics, topology, logic and
    computation: a Rosetta Stone}.  In New Structures for Physics,
  ed.\ Bob Coecke, Lecture Notes in Physics vol. 813, Springer, 2011,
  pp.\ 95--174.
\item
  John C.\ Baez, Tobias Fritz and Tom Leinster.
  \href{http://www.mdpi.com/1099-4300/13/11/1945}{A characterization
    of entropy in terms of information loss}. Entropy \textbf{13}
  (2011), 1945--1957.
\item
  John C.\ Baez and Jason
  Erbele. \href{http://www.tac.mta.ca/tac/volumes/30/24/30-24abs.html}{Categories
    in control}. Th.\ App.\ Cat.\ {\bf 30} (2015), 836--881.
\item
  John C.\ Baez, Brendan Fong and Blake
  Pollard. \href{https://arxiv.org/abs/1508.06448}{A compositional
    framework for Markov processes}. Jour.\ Math.\ Phys.\ {\textbf 57}
  (2016), 033301.
\item
  John C.\ Baez and Blake Pollard.
  \href{https://arxiv.org/abs/1704.02051}{A compositional framework
    for reaction networks}. Rev.\ Math.\ Phys.\ \textbf{29} (2017),
  1750028.
\end{itemize}

%-----------------------------------------
\textbf{Five other significant products}

\vskip 1em

\begin{itemize}
\item
  John C.\ Baez, Irving Segal and Zheng-fang Zhou.  An Introduction to
  Algebraic and Constructive Quantum Field Theory, Princeton
  University Press, 1992.
\item
  John C.\ Baez and James Dolan.
  \href{http://arxiv.org/abs/q-alg/9503002}{Higher-dimensional algebra
    and topological quantum field theory}.  Jour.\ Math.\ Phys. {\bf
    36} (1995), 6073--6105.
\item
  John C.\ Baez. \href{http://arxiv.org/abs/gr-qc/9411007}{Spin
    networks in gauge theory}.  Adv.\ Math.\ {\bf 117} (1996),
  253--272.
\item
  John C.\ Baez.  \href{http://arxiv.org/abs/gr-qc/9709052}{Spin foam
    models}.  Classical and Quantum Gravity {\bf 15} (1998),
  1827--1858.
\item
  John C.\ Baez and Tobias
  Fritz. \href{http://www.tac.mta.ca/tac/volumes/29/16/29-16abs.html}{A
    Bayesian characterization of relative
    entropy}. Th.\ Appl.\ Cat.\ {\bf 29} (2014), 421--456.
\end{itemize}

%--------------------------------------
\textbf{Synergistic activities}

\vskip 1em

\begin{itemize}
\item
  Subcontractor with Metron Scientific Solutions: DARPA's
  \href{https://www.darpa.mil/program/complex-adaptive-system-composition-and-design-environment}{Complex
    Adaptive System Composition and Design Environment} (CASCADE)
  project.
\item
  Organizer: special session on
  \href{https://johncarlosbaez.wordpress.com/2017/09/21/applied-category-theory-at-ucr-part-2/}{Applied
    Category Theory}, Fall Western Sectional Meeting of the AMS, 4--5
  November 2017, U.C. Riverside.
\item
  Founding member:
  \href{http://www.azimuthproject.org/azimuth/show/HomePage}{Azimuth
    Project}, international collaboration of scientists and engineers
  working on environmental problems.
\end{itemize}

\end{document}


% COLLABORATORS AND OTHER AFFILIATIONS:

% \begin{itemize}
% \item
%   Collaborators (co-authors): Abhay Ashtekar (Pennsylvania State U.),
%   Aristide Baratin (Perimeter Institute), Emory Bunn (U.\ Richmond),
%   Jacob Biamonte (Institute for Scientific Interchange), J.\ Daniel
%   Christensen (U.\ Western Ontario), Alejandro Corichi (National
%   Autonomous University of Mexico), Tom Leinster (U.\ Edinburgh),
%   Laurent Freidel (Perimeter Institute), Tobias Fritz (Perimeter
%   Institute), Kirill Krasnov (U.\ of Nottingham), Tom Leinster (U.\ of
%   Edinburgh), Alejandro Perez (Centre de Physique Th\'eorique,
%   Marseille), Michael Shulman (U.\ of Chicago), Mike Stay (Pyrofex
%   Corp.), Urs Schreiber (U.\ Hamburg).
% \item
%   Collaborators (co-editors): Peter May (U.\ of Chicago). 
% \item
%   Graduate advisor: Irving Segal.
% \item
%   Thesis advisees: James Gilliam, Laurel Langford, Alissa Crans,
%   Miguel Carri\'on-Alvarez, Tobias Bartels, Jeffrey Morton, Derek
%   Wise, Alexander Hoffnung, Christopher Rogers, Christopher Walker,
%   Brendan Fong, Jason Erbele, Blake Pollard, Brandon Coya, Kenny
%   Courser, Adam Yassine, Daniel Cicala, Jade Master, Christian
%   Williams, Joseph Moeller.
% \item
%   Postdoctoral scholars sponsored: Daniel Stevenson, Christina Vaisilakopoulou.
% \end{itemize}

% \noindent 13 graduate students advised who have attained degrees, 4
% more currently being advised, and 2 postdoctoral students sponsored.
