\documentclass[12pt,letterpaper]{amsart}

\sloppy

\addtolength{\textwidth}{60pt}
\addtolength{\oddsidemargin}{-32pt}
\evensidemargin\oddsidemargin

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

%PACKAGES
\usepackage{geometry}               
\geometry{letterpaper}                   

%URL colors
\usepackage{color}
\definecolor{myurlcolor}{rgb}{0.6,0,0}
\definecolor{mycitecolor}{rgb}{0,0,0.8}
\definecolor{myrefcolor}{rgb}{0,0,0.8}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks,
  linkcolor=myrefcolor,
  citecolor=mycitecolor,
  urlcolor=myurlcolor}

\begin{document}

\centerline{\large CURRENT AND PENDING SUPPORT}
\vskip 1em
\centerline{David I.\ Spivak}

\vskip 1em
\vskip 1em

\textbf{Current Support:}

\begin{enumerate}
\item
  Project Title: Category-Theoretic Approaches for the Analysis of
  Distributed Systems. \hfill \break Source of Support: NASA. \hfill
  \break Project Location: Massachusetts Institute of
  Technology. \hfill \break Total Award Amount: \$300,000. \hfill
  \break Starting Date: 06/01/2014.\hfill \break Ending Date:
  10/31/2014.\hfill \break Person-months Per Year Committed to the
  Project: \hfill \break Calendar: 0.833, Academic: 0.625, Summer:
  0.208
\vskip 1em
\item
  Project Title: Categorical Approach to Agent Interaction. \hfill
  \break Source of Support: AFOSR. \hfill \break Project Location:
  Massachusetts Institute of Technology.  \hfill \break Starting Date:
  12/01/2013. \hfill \break Ending Date: 11/30/2018.\hfill \break
  Person-months Per Year Committed to the Project: \hfill \break
  Calendar: 1.500, Academic: 1.125, Summer: 0.375
\vskip 1em
\item
  Project Title: Pixel Matrices and Other Compositional Analyses
  of Interconnected Systems. \hfill \break Source of Support:
  AFOSR. \hfill \break Project Location: Massachusetts Institute of
  Technology. \hfill \break Starting Date: 12/01/2016.\hfill \break
  Ending Date: 11/30/2019.\hfill \break Person-months Per Year
  Committed to the Project: \hfill \break Calendar: 1.667, Academic:
  1.250, Summer: 0.417
\end{enumerate}

\textbf{Pending Support:}

\begin{enumerate}
\item
  Project Title: Higher Order Probabilistic Temporal Logic for the
  Verification of Autonomous Systems.
  \hfill \break
  Source of Support: AFOSR
  \hfill \break
  Project Location: Massachesetts Institute of Technology.
  \hfill \break
  Period: 08/01/2018 through 07/31/2020
  \hfill \break
  Person-months Per Year Committed to the Project:
  \hfill \break
  Calendar: 2.88 (year 1), 3.48 (year 2)
  \vskip 1em
\item
  Project Title: Pixel matrices and other compositional analyes of
  interconnected systems. (Supplement)
  \hfill \break
  Source of Support: AFOSR
  \hfill \break
  Project Location: Massachesetts Institute of Technology.
  \hfill \break
  Period: 06/01/2018 through 05/31/2019
  \hfill \break
  Person-months Per Year Committed to the Project:
  \hfill \break
  Calendar: 0.36 
  \vskip 1em
\end{enumerate}

\end{document}
